Sparse Function-space Representation \\ of Neural Networks

### 2023-05-15 paper/main.tex
moved rl stuff to appendix
added to rl section in exeriments

\subsection{Reinforcement learning}
A key challenge in RL is balancing the trade-off between exploration and exploitation.
That is, should the agent select an action that it knows will lead to a high reward (exploitation), or should it
hope to discover new actions which lead to high reward (exploration) by selecting actions that it has not selected before.
In this section, we demonstrate  that our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.

See \cref{app:rl} for more details of our experiments.

We compare a model-based RL agent using a simple MLP dynamic model with
\begin{itemize}
  \item uncertainty is good for exploration
\end{itemize}

>>>>

\subsection{Reinforcement learning}
A key challenge in RL is balancing the trade-off between exploration and exploitation.
That is, should an agent select actions that it knows will lead to a high reward (exploitation), or should it
hope to discover new actions which lead to high reward (exploration)?
In this section, we show that \our's uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim,
demonstrating the quality of our uncertainty estimates.
% In this section, we demonstrate  that our method's principled uncertainty estimates can be used to balance this trade-off in a model-based RL algorithim.
We refer the reader to \cref{app:rl} for an overview of the problem and details of our experiments.

Cart pole swing up task in MuJoCo \cite{todorov2012mujoco}
We compare our method with deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} -- a model-free RL baseline --
which is sample inefficient.
We test our model's uncertainty estimates by comparing it to using Laplace-GGN with GLM predictions, using an ensemble of neural networks
(with different initialisations),
To ensure a fair comparison, we use the same MLP architecture/training scheme and we keep the same model-based RL algorithm.
See \cref{app:rl} for more details of our experiments.

We also compare to deep deterministic policy gradient (DDPG) \cite{lillicrapContinuousControlDeep2016} -- a model-free RL baseline --
which we expect to be much more sample inefficient.
